---
title: "My Fancy Presentation"
author: "Ioana Marinica"
date: "9/16/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



## My new slide
Some content on it.

***
A slide without a title.




## My title

### A top level subheading

#### A second level subheading




## List

- Bullet one
- Bullet two

1. Item a
2. Item b



## Formatting

*italic*

**bold**

`for (i %in% 1:10)`


## Code to be run

```{r}
head(mtcars)
```


## Code without comment characters

```{r, comment = ""}
head(mtcars)
```

## Code including the code itself

```{r, comment = "", echo=TRUE}
head(mtcars)
```

## Just code without running (evaluating) it

```{r, comment = "", eval=FALSE, echo=TRUE}
head(mtcars)
```

## Graph slide

```{r, echo = FALSE, fig.align='center', fig.cap='My awesome figure!'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```




## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

